\section{Conclusion and Future Work}
\label{sec:conclusion-and-future-work}

In this project, we addressed the limitations of existing game engines when used for general purpose interactive media
and established issues with performance, scalability, and maintainability in such use cases.
Upon analysis, we explored alternative approaches and developed a custom engine built upon the ECS framework with an
emphasis on reducing abstraction and overhead, while still providing a flexible and scalable foundation for interactive
media development.
As an evaluation of the engine's efficiency in real-world conditions, we developed a bullet hell game and rhythm game
hybrid system with real-time input handling, precise timing, and large numbers of objects.
We also benchmark the engine's core logic processing in comparison to existing ECS libraries to evaluate the difference
in performance with industry standards.
The results show potential in the use of this engine for effective and maintainable interactive media development, as well
as being sufficiently versatile across different domains of such media.

Future work may involve expanding the engine's ECS logic to encompass more common ECS programming paradigms, such as
more powerful query support and query iteration across the ECS resources directly from the system.
The engine itself can also serve as the foundation for more extensive research towards ECS optimization techniques.
One such technique is the compile-time determination of multithreaded system execution order via the creation of
a system dependency graph, which will greatly increase performance when multiple systems are concerned.
The game developed as the case study will be continually improved upon and be launched as a full game in the future.

\label{tag:end}