\section{Ethic, Privacy, and Professional Consideration}
\label{sec:ethic-privacy-and-professional-consideration}

\subsection{Ethical Issues}
\label{subsec:ethical-issues}

The project's system was developed from the ground up with lightweight and open-source libraries such as DDS and miniaudio for asset processing.
Due to its minimal model, data privacy for users is secured and well encapsulated within the application.
Additionally, this project utilizes aggressive compile-time optimizations to maintain high-performance on par with
the industry standard.
Thus, allowing the framework to run efficiently across varying hardware specifications, eliminating most hardware entry barriers.
System safety and reliability are ensured through a well-customized memory management system and modular architecture
along with system testing to reduce unexpected behavior.


\subsection{Standards \& Laws}
\label{subsec:standards-&-laws}

The project mostly references the verified official documentation, including DirectX and Microsoft C++ documentation,
as well as credible research and articles on engine architecture and game design theory.
All development and design are supported by reliable and recognized sources in software engineering
and game development literature, ensuring grounded and reliable information.
Additionally, the project complies with the licensing agreements for all other third-party open-source libraries
used for audio and rendering to ensure legal reliability.

\subsection{Environmental Impact}
\label{subsec:environmental-impact}
The project provides lightweight architecture and performance-oriented system design
to reduce unnecessary computational overhead and resource consumption.
Furthermore, the framework runs efficiently across varying hardware specifications, which may potentially
reduce hardware upgrade requirements, expending the lifespan of the user's existing hardware.


\subsection{Intellectual Property}
\label{subsec:intellectual-property}

All codes, tools and assets created during the project are original works owned by the team.
DirectX and Microsoft's Window’s APIs used in this project are free to use without any attribution so long as there is
no binary tampering or falsely acclaimed trademark usage.
This project uses miniaudio for audio processing, which is licensed under Public Domain and MIT No Attribution, 
allowing for free use, modification, and distribution without attribution or licensing fees~\cite{MIT0License}.
All visual and audio assets are self-produced.
The project complies with software licensing terms and university policies regarding intellectual property and academic integrity.
This project is licensed under the MIT License, protected under Thai Copyright Act B.E.2537.
The project's engine is licensed under CC BY-NC 4.0 as the team allows users to distribute, remix, adapt, and build upon
the material in any medium or format for research or noncommercial purposes only,
and only so long as attribution is given to the creator~\cite{CreativeCommonsLicense}.