\subsection{Analysis}
\label{subsec:analysis}

Table~\ref{tab:system-frame-duration-benchmark} shows the measured system frame duration for each ECS implementation
across increasing entity counts.
In all cases, frame duration increases approximately linearly with respect to the number of entities.
This indicates that each framework scales proportionally with workload size and does not exhibit
significant nonlinear overhead within the tested range.

Among the evaluated implementations, the custom engine demonstrated significantly lower execution times than both
general-purpose ECS frameworks among all entity counts.
At 16,000 entities, the custom engine was approximately 4.9 times faster than Bevy ECS and approximately 8.8 times faster than EnTT\@.
This result is attributable to the reduced abstraction overhead and compile-time fixed-component specializations present
in the custom engine compared to the runtime dynamic-component architectures of Bevy ECS and EnTT\@.

The relatively linear growth across all implementations suggests that the benchmark workload is dominated
primarily by system iteration cost rather than synchronization, scheduling, or memory management bottlenecks.
No abrupt increases in frame duration were observed as the entity count increased, indicating stable scaling behavior
within the tested range.

Overall, the results indicate that the custom engine provides the highest execution performance for the evaluated
workload among the tested ECS frameworks.

\subsection{Limitations}
\label{subsec:limitations-and-lessons}

The evaluated workload is a simple process that depends only on iteration and data modification.
It does not factor in the other aspects of an ECS architecture, such as the querying of entity archetypes and
the adding and removing of components and entities.
This means that we cannot properly measure the performance of the custom engine in those aspects in comparison to
general-purpose architectures.

This test was performed in the language's debug build profile.
With the release build profile, the well-established ECS architectures could take advantage of more aggressive compiler optimizations.
Informal testing indicated that the custom engine would be able to provide a competitive performance
to the other tested frameworks, being approximately 1.3 times slower than EnTT and 1.6 times slower than Bevy ECS\@.