\section{Risk and Resource Management}
\label{sec:risk-and-resource-management}

\subsection{Risks}
\label{subsec:risk}

The major risk of this project is its scope compared to the development timeframe.
The complexity and workload of developing both the custom game engine and game development are considerably high.
Additionally, work distribution was challenging to manage due to higher-level development depending on the progress of
engine systems development; thus, creating a development bottleneck, especially at the early phase of development.
To mitigate, the lower-end development provides early features or APIs for higher-level developers to test and develop
some game systems in parallel.
\\\\
As the project is developed from the ground up, errors from the lowest level may cause sequential instability in higher-level systems.
Therefore, testing is required at every stage of the development to ensure system stability.


\subsection{Adaptations}
\label{subsec:adaptations}

Because of the project's large scope compared to the development timeframe, many planned functionalities were postponed for
future works to prioritize optimizing the core systems.
Additionally, gameplay development workloads were frequently adjusted to utilize parallel development
while waiting for features from the engine-level systems.


\subsection{Resources}
\label{subsec:resources}

The project utilizes personal computer systems with standard CPUs and GPUs that are compatible with DirectX 11
for development, testing, and performance evaluation.
C++20, DirectX 11, Windows API, and GoogleTest are used for development, rendering, debugging and testing.
Additional lightweight open-source libraries such as DirectDraw Surface and miniaudio are utilized for asset and audio processing.
Developers may use any preferred text editor, mostly CLion and neoVim.
GitHub and Discord were used for collaboration purpose.
This project require no additional financial expenses as general hardware resources were already available to the development team.


\subsection{Cost Considerations}
\label{subsec:cost-considerations}

The project requires no additional development cost since the project were made entirely from the ground up
using C++, Windows APIs, DirectX and free open-source libraries.
The hardware resources used for development and testing were already available to the development team since the project started.

