
% /_\ Nack should check: combine two sections into one "Project management and teamwork"

\subsection{Work Division}
\label{subsec:work-division}

Since this project is large and requires highly specialized personnel, each task was assigned
to each person with the intent for them to be the master pertaining to that aspect of the system.
Each of the tasks has their own set of challenges and requires very deep understanding.
This means each person would have their own hard and easy tasks where, on higher-level management,
it can be inferred that the workload is already balanced because of the need of specialty.

\subsection*{Project Lead}
The person with this role will manage and plan the project.
The main task of this person is to create a systematic plan for the project which is tangible and able to lead to the finished product.
Not only that, this person also needs to communicate and also contact insiders and outsiders as needed.
Also, this person must be able to communicate with other team members, come to an understanding, and be able to find a
suitable solution to make the work go smoothly as much as possible.
\\\\
Since this team is a small team, the project lead must be able to direct the project direction and understand the image
of the final product so that they can achieve the most beneficial outcome for the team.

\subsection*{System Software Architect}
The person with this role is responsible for system design.
They have the responsibility to design an architecture which is
suitable for the needs of the software.
They must also create a good work environment for the team to work
with using this system.

\subsection*{Gameplay Designer}
The person with this role is responsible for designing a game which can test whether
the system is working as intended or not.

\subsection*{Game Software Engineer}
The person with this role has the task to implement the game according to gameplay design
using the structure planned by the Gameplay Software Architect.

\subsection*{Graphic Software Engineer}
The person with this role works on creating graphics with high fidelity and also works
on optimization for the graphic section of the software, such as GPU Memory Management.

\subsection*{Operating System Software Engineer}
The person with this role works on implementing the Application Programming Interface (API) to communicate with
the operating system safely and optimally.
Also, this person must ensure the software security and memory safety.

\subsection*{User Level Software Engineer}
The person with this role works on implementing the API for users to write software on this system.
The person in charge must be able to create an API that is easy to implement and use.

\subsection*{Gameplay Software Architect}
This person with this role designs the system flow of a game to ensure good user experience
and also optimal data flow within the game system.

\subsection{Communication}
\label{subsec:collaborative-plan}
We have a group meeting for updating progress and planning on Friday of every week.
We also have a meeting with the advisor on Thursday of every week.
If there is a need to be absent, every person needs to clearly state so beforehand.
Each system planning will be planned as sprints with durations of two weeks per each iteration.
After every iteration, we will have a reflection on the first Friday after the end of iteration.
For meeting, everyone on the team has selected to have meetings in online format on Discord.
\\\\
For project source code management, we use Git Version Control System and GitHub as
a remote repository.
The project source code will contain only system source code, game source code, document, report and report image only.
Game resources will need to be downloaded outside the repository.
\\\\
We use Cmake as a build system to allow team members to work easily with any text editor.
We also use clangd as a formatter to have a consistent coding style.
MSVC is used as a main system compiler such that we target Windows Operating System specifically.
Although we allow any text editor to use within this project, Clion by JetBrains is preferred.

\subsection{Reflection}
\label{subsec:reflection}

% Assess strengths, weaknesses, and improvements in teamwork.
Due to the work being split based on the strengths of each team member, each person found their tasks to be challenging
but not overly difficult.
As such, the implementation of each system in detail was fast and performant.
For sections of the task where the person responsible was not overly familiar, they could source information from related fields
in their expertise to help with the issue.
They were also able to correctly query and verify search engines and large language models for accurate information.

However, since much of the work was done in isolation, communication between modules suffered minor issues.
Each person was hesitant to contribute to the other's works to ensure the connections between modules were smooth and efficient.
Some might have found it easier to accept the work of the expert rather than discuss corrections to their work.
This was mitigated by the team leader facilitating meetings and reviews of each person's work, and the project was
completed within the predicted duration in the end.