\section{Testing and Experimentation}
\label{sec:testing}

\subsection{Methodology}
\label{subsec:methodology}

The purpose of the testing is to evaluate the performance characteristics of our custom engine in comparison with industry-standard
ECS frameworks under comparable workloads.
We assess performance through measuring system frame duration, the time required to run the user system,
as this duration is a direct indicator of runtime responsiveness and execution efficiency.

For each framework, system frame duration is measured by recording a timestamp immediately before the execution of
the user system and another immediately after the user system finished processing.
We repeat this process for different entity counts to observe underlying performance degradation.
To evaluate the framework performance, we assume an instantaneous, highly optimized renderer.
To this end, we exclude the rendering systems from Bevy and our custom engine, opting to compare only the logical systems.
This lets us take the system frame duration to be representative of the response time from input to output,
making it an effective metric for overall system performance.

All ECS frameworks were tested using the language’s release build profile.
Systems for each framework were implemented according to official tutorials and documentation
to ensure that implementations were idiomatic and representative of recommended usage patterns.
We average the system frame time across 1000 repetitions to remove noise from the result.
The output is logged only after all time-sensitive work is done to not impact performance.

All tests were executed on local hardware using the same machine and operating environment to ensure consistency across measurements.
The hardware specifications are as follows:

\begin{itemize}
    \item CPU: 11th Gen Intel(R) Core(TM) i7-11800H @ 2.30 GHz
    \item GPU: Intel(R) UHD Graphics
    \item Memory: 3200 MHz 16.0 GB RAM
    \item Operating System: Windows 10 Version 22H2 (OS Build 19045.6466)
\end{itemize}

When testing ECS frameworks, it is important that the user system implementation itself does not have a massive time cost relative to
the framework.
With consideration of this, we opted for a relatively simple process, instead of the logic used for complex simulations.
The user system used for the benchmark is a process that adds an entity's velocity to its position.
This system measures the framework's efficiency in iteration and data modification, which constitutes a large part of ECS usage.

\subsubsection*{Bevy ECS}

For the Bevy ECS implementation, timing measurements are performed using the Rust standard library's \texttt{std::time::Instant}.
A benchmarking resource is defined to store frame timing information and maintain a handle to a log file for persistent output.

Two benchmark systems are inserted into the Bevy update schedule: one system records the start timestamp immediately
before execution of the user-defined systems, while another records the end timestamp immediately afterward.
Bevy’s system chaining mechanism is used to guarantee deterministic execution order between the
benchmark systems and the systems under test.
Each user system is allowed to be parallelized by Bevy's ECS scheduler.
To idiomatically measure only user systems and minimize additional overhead, we use Bevy's \texttt{MinimalPlugins} plugin group.
According to related documentation~\cite{bevy_minimalplugins}, this plugin group represents the absolute minimum bare-bones application.

The elapsed duration between the two timestamps was written both to standard output and to a log file after the system
has run to the specified number of repetitions.
We use \texttt{std::fs::File} guarded by a mutex for safe access.

\subsubsection*{EnTT}

For the EnTT implementation, timing measurements were performed using C++’s \texttt{<chrono>} library.
The benchmark instrumentation was placed directly within the main \texttt{update()} function responsible for
executing all ECS systems.
We let this function return the duration measured by the benchmark to store and use for the time difference.
We use a for-loop to repeat this function for the specified number of repetitions.
For the user system, we use a range-for implementation as documented in the framework's given code example~\cite{ValtoLibraries_EnTT}.

A timestamp was recorded immediately before system execution using \texttt{std::chrono::steady\_clock::now()},
and a second timestamp was recorded immediately after all systems completed execution.
The elapsed duration was converted to microseconds using \texttt{std::chrono::duration\_cast}.

Test parameters and measured frame times were appended to a persistent log file using \texttt{std::ofstream},
as well as the final average.

\subsubsection*{Our Custom Engine}

For our custom engine, we use the ECS header files to construct the benchmarking program.
In the main function, we construct a \texttt{TaskManager} which registers the user system to run.
We then create a helper function that applies the benchmark instrumentation before and after
a call to the \texttt{TaskManager::update()}, returning the duration elapsed to store and use for the time difference.
We use a for-loop to repeat this function for the specified number of repetitions.

Test parameters and measured frame times were appended to a persistent log file using \texttt{std::ofstream},
as well as the final average.
The general mechanisms, outside of framework implementations, are kept identical to the EnTT case for parity.